Modeling the Evolution of Mimicry

### 2016-02-29 docs/paper/Paper.tex
Final Changes

The framework consists of a three dimensional world where agents get complete freedom of movement defined from their genetic representation. This toroidal \textbf{space} is a three-dimensional lattice of discrete points, divided in multiple cells, which can be visualized. A \textbf{cell} is a three dimensional cubical section of the hyperspace. The purpose of the cells is to avoid expensive distance calculations. As two agents are considered \textsl{``close"} to interact when they are in the same cell and \textsl{``distant"} otherwise. \textbf{Time}, being an integer \( (t \geq 0) \), advances in discrete steps in the simulation, where at each step the agents update themselves.

@@

The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for 10000 iterations. With the initial configuration in the above table we can observe that multiple rings of prey population have been created. Two prey species are considered to be in a ring if their CA pattern have Hamming distance within 10 bits. Population of palatable species have been represented with line curve while population of unpalatable species have been presented with dotted curve. Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population. The simulation was initiated with two prey species having CA rule of 110 and 30 and being palatable and unpalatable respectively. Over time the population of CA Rule 30 dominates the population (Figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable. Similarly a palatable population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 4000 approx.). CA Rule 110 was initialized as a set of palatable species.

>>>>

The framework consists of a three dimensional world where agents get complete freedom of movement defined from their genetic representation. This toroidal \textbf{space} is a 3D lattice of discrete points, divided in multiple cells, which can be visualized. A \textbf{cell} is a three dimensional cubical section of the hyperspace. The purpose of the cells is to avoid expensive distance calculations. As two agents are considered \textsl{``close"} to interact when they are in the same cell and \textsl{``distant"} otherwise. \textbf{Time}, being an integer \( (t \geq 0) \), advances in discrete steps in the simulation, where at each step the agents update themselves.

@@

The plot in Figure \ref{fig:plot-2-prey} is simulation time verses prey population after running it for 10000 iterations. With the initial configuration in the above table we can observe that multiple rings of prey population have been created. Two prey species are considered to be in a ring if their CA pattern have Hamming distance within 10 bits. Population of palatable species have been represented with line curve while population of unpalatable species have been presented with dotted curve. Different signs of squares, triangles and diamonds have been used to distinguish between species of prey population. The simulation was initiated with two prey species having CA rule of 110 and 30, being palatable and unpalatable respectively. Over time the population of CA Rule 30 dominates the population (Figure \ref{fig:plot-2-prey}) as most predators recognize it as unpalatable. Similarly a palatable population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 4000 approx.). CA Rule 110 was initialized as a set of palatable species.
